%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Conclusion
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Conclusion}
\label{sec:conclusion}

We have shown that Bernoulli sets are closed under all four set-theoretic operations: complement, union, intersection, and set difference.
Each operation yields a (possibly higher-order) Bernoulli set whose error rates are closed-form functions of the operand rates and set cardinalities.
The resulting collection of Bernoulli sets forms commutative monoids under union and intersection, with the empty set and universal set serving as identity elements.
Relational predicates---subset and equality---admit exact probability formulas that factorize element-wise.
An interval arithmetic extension propagates uncertain rate parameters through set operations, yielding guaranteed bounds when parameters are only approximately known.

\paragraph{Practical implications.}
A practitioner building a system on Bloom filters need not re-derive the error analysis for each new combination of filters: the composition theorems of \cref{sec:set_theory} apply immediately, yielding closed-form error rates and confidence intervals for any set-theoretic expression.

\paragraph{Open problems.}
The partition weights $w_1, w_2, w_3$ in the set-operation formulas require knowledge of the objective set cardinalities, which are typically unknown (\cref{rem:unknown_partitions}).
Developing principled estimators for these cardinalities from the approximate sets themselves, with quantified bias and variance, is a natural next step.

\paragraph{Companion papers.}
The Bernoulli set model, including the axioms, error-count distributions, asymptotic limits, confidence intervals, and higher-order composition theorem, is developed in~\cite{bernoulliSets}.
The probability distributions of binary classification measures (positive predictive value, negative predictive value, accuracy, Youden's $J$) are derived in~\cite{bernoulliMeasures}.
The joint entropy of error counts and the information-theoretic space complexity lower bound are developed in~\cite{bernoulliEntropy}.
